---
title: "Boxplot hydrologic metrics"
output: html_document
---

```{r }

if ((Sys.info()["nodename"]) == "COP026") {
  dir_data <- "C:/Users/arvor_d/Documents/workwork/data"
  dir_plot <- "C:/Users/arvor_d/Documents/workwork/plot"
} else if ((Sys.info()["nodename"]) == "COSTELSV6") {
  dir_data <- "F:/kamir_e/$data"
  dir_plot <- "F:/kamir_e/$plot"
}

```

## Library

```{r }

library(plyr)
library(tidyverse)
library(tidyr)
library(dplyr)
library(maps)
library(ggplot2)
library(sp)
library(rgdal)
library(raster)
library(ggmap)
library(sf)
library(viridis)

```

## PARAMETERS

```{r }

# foret = 3, savanna = 4, pasture = 15, soybean = 39, other temp.crops = 41, per.crops = 36

time_laps <- c(1985:2019)
year=2019
y <- which(time_laps==year)

basin_select <- st_read(file.path(dir_data, "hydroshed", "basin_select.shp"))

```

## LOADING & MERGING files


```{r }

list_hydro <- list()

i=0

for (basin_id in basin_select$HYBAS_ID){
  
    i=i+1
    

    WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]

    list_hydro[[i]] <- get(load(file=file.path(WD.tmp, paste0("hydrometric_",basin_id,".RData"))))
    
    list_hydro[[i]]$maj <- NA
    
    df_lsm <- get(load(file=file.path(WD.tmp, paste0("mapbiomas_lsm_",basin_id,".RData")))) %>% mutate(ID=basin_id) 
    
    perc_past <- (df_lsm %>% filter(ID==basin_id, class==15, metric=='pland', layer==y))$value
    perc_crop <- (df_lsm %>% filter(ID==basin_id, class==39, metric=='pland', layer==y))$value 
    
    if(is_empty(perc_past)){perc_past=0}
    
    if(is_empty(perc_crop)){perc_crop=0}
    
    #if(perc_crop!=0|perc_past!=0){
      
        if(perc_past>=50){
        
        list_hydro[[i]]$maj <- 'pasture'
      }
    
      if(perc_crop>=50){
        
        list_hydro[[i]]$maj <- 'soybean'
      }

    #}
  
    
    

}

df_hydro <- do.call("rbind",list_hydro) %>% drop_na()

dim(df_hydro)

```

## Statistical tests

Importance de la taille de l'échantillon: pvalue inf 5% sur petit échantillon est plus significatif que pvalue sup 5%

```{r }

df_crop_hydro <- df_hydro %>% filter(maj=='soybean') %>% dplyr::select(d.rios)
df_past_hydro <- df_hydro %>% filter(maj=='pasture') %>% dplyr::select(d.rios)

# 1. Normality: h0: population suit loi normale. rejetée si pvalue inf à 5%
shapiro.test(unlist(df_crop_hydro))
shapiro.test(unlist(df_past_hydro))

ggplot(df_hydro %>% filter(maj=='soybean'))+
  geom_histogram(aes(x=d.rios))

ggplot(df_hydro %>% filter(maj=='pasture'))+
  geom_histogram(aes(x=d.rios))


# 2. Wilcoxon: distributions: h0: meme loi, si pvalue inf à 5% rejetée 
wilcox.test(unlist(df_past_hydro), unlist(df_crop_hydro))

```

## BOXPLOTTING

We compute boxplots of % of lost forest, for the two main agriculture types: pasture or crops

```{r }


ggplot(df_hydro) + 
  geom_boxplot(aes(x=factor(maj),y=d.rios, group=maj, fill=factor(maj)), show.legend = FALSE, alpha=0.2) +
  scale_y_continuous(limits = quantile(df_hydro$d.rios, c(0.1, 0.9)))+ 
  labs(title = paste0("d.rios per hydrobasin"), x="", y="")+ 
  theme_bw()+
  theme(axis.text.x = element_text(size = 12), axis.title.x = element_text(size = 10, vjust = 1.5, hjust=1),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 10, angle = 0, vjust=1.05),
        plot.title = element_text(size = 10, face = "bold", hjust=0.5))

ggsave(file.path(dir_plot, paste0("d.rios.boxplot.pdf")), dpi = 300)

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.









