---
title: "Boxplot of hydrographic metrics"
output: html_document
---

We plot hydrographic metrics (d.rios = stream density, d.nascente = spring density, d.reserv = reservoir density) sumarized in "lsm_sumup_hydro" code.
Crop / pasture distinction for each basin is based on their area percentage related to the deforested area.

## Directories

```{r }

if ((Sys.info()["nodename"]) == "COP026") {
  dir_data <- "C:/Users/arvor_d/Documents/workwork/data"
  dir_plot <- "C:/Users/arvor_d/Documents/workwork/plot"
} else if ((Sys.info()["nodename"]) == "COSTELSV6") {
  dir_data <- "F:/kamir_e/$data"
  dir_plot <- "F:/kamir_e/$plot"
}

```

## Library

```{r }

library(plyr)
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
library(sp)
library(rgdal)
library(ggmap)
library(sf)

```

## PARAMETERS

```{r }

# foret = 3, savanna = 4, pasture = 15, soybean = 39, other temp.crops = 41, per.crops = 36

time_laps <- c(1985:2019)
year=2019
y <- which(time_laps==year)

basin_select <- st_read(file.path(dir_data, "hydroshed", "basin_select.shp"))

```

## LOADING dataset

```{r }

# lsm on nascente buffer
df_hydro <- get(load(file=file.path(dir_plot, paste0("df_hydro_cropast.RData"))))

```


## Statistical tests

Great importance of sample size: on small sample pvalue inf 5% (rejecting hypothesis) is strong

!!Warning!! metric of interest (d.rios, d.reserv, or d.nascente) should be manually set.

```{r }

df_crop_hydro <- df_hydro %>% filter(maj=='soybean') %>% dplyr::select(d.rios) # set metric
df_past_hydro <- df_hydro %>% filter(maj=='pasture') %>% dplyr::select(d.rios) # set metric

# 1. Normality: h0: population suit loi normale. rejetée si pvalue inf à 5%
shapiro.test(unlist(df_crop_hydro))
shapiro.test(unlist(df_past_hydro))

ggplot(df_hydro %>% filter(maj=='soybean'))+
  geom_histogram(aes(x=d.rios)) # set metric

ggplot(df_hydro %>% filter(maj=='pasture'))+
  geom_histogram(aes(x=d.rios)) # set metric


# 2. Wilcoxon: distributions: h0: meme loi, si pvalue inf à 5% rejetée 
wilcox.test(unlist(df_past_hydro), unlist(df_crop_hydro))

```

## BOXPLOTTING

!!Warning!! metric of interest (d.rios, d.reserv, or d.nascente) should be manually set.

```{r }


ggplot(df_hydro) + 
  geom_boxplot(aes(x=factor(maj),y=d.nascente, group=maj, fill=factor(maj)), show.legend = FALSE, alpha=0.2) + # set metric
  scale_y_continuous(limits = quantile(df_hydro$d.nascente, c(0.1, 0.9)))+ # set metric
  labs(title = paste0("d.nascente per hydrobasin"), x="", y="") + # set metric
  theme_bw()+
  theme(axis.text.x = element_text(size = 12), axis.title.x = element_text(size = 10, vjust = 1.5, hjust=1),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 10, angle = 0, vjust=1.05),
        plot.title = element_text(size = 10, face = "bold", hjust=0.5))

ggsave(file.path(dir_plot, paste0("d.nascente.boxplot.pdf")), dpi = 300) # set metric

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.









