---
title: "Boxplotting forest riparian vs basin"
output: html_document
---

We plot forested areas at basin and riparian levels, summarized in "lsm_sumup_rios" code.
Crop / pasture distinction for each basin is based on their area percentage related to the deforested area.


```{r }

if ((Sys.info()["nodename"]) == "COP026") {
  dir_data <- "C:/Users/arvor_d/Documents/workwork/data"
  dir_plot <- "C:/Users/arvor_d/Documents/workwork/plot"
} else if ((Sys.info()["nodename"]) == "COSTELSV6") {
  dir_data <- "F:/kamir_e/$data"
  dir_plot <- "F:/kamir_e/$plot"
}

```

## Library

```{r }

library(plyr)
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggmap)
library(sf)

```

## PARAMETERS

```{r }

# foret = 3, savanna = 4, pasture = 15, soybean = 39, other temp.crops = 41, per.crops = 36

time_laps <- c(1985:2019)
year=2019
y <- which(time_laps==year)
tampon=100

basin_select <- st_read(file.path(dir_data, "hydroshed", "basin_select.shp"))

```

## LOADING datasets

```{r }

# lsm on whole basin
df_basin_foret <- get(load(file=file.path(dir_plot, paste0("df_basin_foret4rios_",tampon,".RData"))))

# lsm on rios buffer
df_rios_foret <- get(load(file=file.path(dir_plot, paste0("df_rios_foret_", tampon, ".RData"))))

```

## Whole basin statistical tests

Great importance of sample size: on small sample pvalue inf 5% (rejecting hypothesis) is strong

```{r }

df_crop_bas <- df_basin_foret %>% filter(maj=='soybean') %>% dplyr::select(value)
df_past_bas <- df_basin_foret %>% filter(maj=='pasture') %>% dplyr::select(value)

# 1. Normality

ggplot(df_basin_foret %>% filter(maj=='soybean'))+
  geom_histogram(aes(x=value))

ggplot(df_basin_foret %>% filter(maj=='pasture'))+
  geom_histogram(aes(x=value))

shapiro.test(unlist(df_crop_bas))
shapiro.test(unlist(df_past_bas))

dim(df_crop_bas) # 158 obs
dim(df_past_bas) # 185 obs

# 2. Test Student (moyenne)

t.test(unlist(df_past_bas), unlist(df_crop_bas))

# 2. Test Wilcoxon (distribution)

wilcox.test(unlist(df_past_bas), unlist(df_crop_bas))

```

## Rios buffer statistical tests

Importance de la taille de l'échantillon: pvalue inf 5% sur petit échantillon est plus significatif que pvalue sup 5%

```{r }

df_crop_rios <- df_rios_foret %>% filter(maj=='soybean') %>% dplyr::select(value)
df_past_rios <- df_rios_foret %>% filter(maj=='pasture') %>% dplyr::select(value)

# 1. Normality

ggplot(df_rios_foret %>% filter(maj=='soybean'))+
  geom_histogram(aes(x=value))

ggplot(df_rios_foret %>% filter(maj=='pasture'))+
  geom_histogram(aes(x=value))

shapiro.test(unlist(df_crop_rios))
shapiro.test(unlist(df_past_rios))

dim(df_crop_rios) # 158 obs
dim(df_past_rios) # 185 obs

# 2. Test Student (moyenne)

t.test(unlist(df_past_rios), unlist(df_crop_rios))

# 2. Test Wilcoxon (distribution)

wilcox.test(unlist(df_past_rios), unlist(df_crop_rios))

```

## BOXPLOTTING


```{r }

# building df
df_bv <- df_basin_foret %>% mutate(scale='basin') %>% dplyr::select(value, maj, scale)
df_rv <- df_rios_foret %>% mutate(scale='riparian buffer') %>% dplyr::select(value, maj, scale)
 
df_tot <- rbind(df_bv, df_rv) %>% dplyr::rename('farming.type'='maj')

# plotting
ggplot(df_tot,aes(factor(scale, levels=c('basin','riparian buffer')), value) ) + 
  geom_boxplot(aes(col=farming.type), show.legend = TRUE, alpha=1.2) +
  scale_y_continuous()+
  #scale_color_manual(values=c("#FF9999", "blue2"))+
  scale_color_brewer(palette="Dark2")+
  labs(x="", y="% forested area")+ 
  theme_bw()+
  theme(axis.text.y = element_text(size = 10), axis.title.y = element_text(size = 10,  vjust=0.99), axis.ticks.x = element_blank())

ggsave(file.path(dir_plot, paste0(year, "_rios_basin_buf",tampon,".boxplot.pdf")), dpi = 300)


```