---
title: "file preparation"
output: html_document
---

We crop all data on each of the basin shape. There is land use data (MapBiomas and Modis), and hydrographic data (springs, single streams, polyline streams, and reservoirs).

## Directories

```{r }

if ((Sys.info()["nodename"]) == "COP026") {
  dir_data <- "C:/Users/arvor_d/Documents/workwork/data"
  dir_plot <- "C:/Users/arvor_d/Documents/workwork/plot"
} else if ((Sys.info()["nodename"]) == "COSTELSV6") {
  dir_data <- "F:/kamir_e/$data"
  dir_plot <- "F:/kamir_e/$plot"
}

```

## Library

```{r }

library(plyr)
library(tidyverse)
library(tidyr)
library(dplyr)
library(foreach)
library(iterators)
library(parallel)
library(doParallel)
library(maps)
library(ggmap)
library(sf)
library(terra)

```


## Loading selected sub basin files 

```{r }

basin_select <- st_read(file.path(dir_data, "hydroshed", "basin_select.shp"))

```

## MAPBIOMAS cropping

```{r }

# Mapbiomas raster for whole MT
mapbiomas_full <- rast(file.path(dir_data, "mapbiomas", "biomas1985_2019_mg.tif"))

# Cropping
tictoc::tic()

for (basin_id in basin_select$HYBAS_ID){
 
  ligne <- which(basin_id==basin_select$HYBAS_ID)
  mapbiomas_crop <- terra::crop(mapbiomas_full,basin_select[ligne,])
  mapbiomas_mask <- terra::mask(mapbiomas_crop,vect(basin_select[ligne,]))
  mapbiomas_mask_utm <- terra::project(mapbiomas_mask,"+init=epsg:32721",method="ngb")

  WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]

  terra::writeRaster(mapbiomas_mask_utm, file.path(WD.tmp, paste0("mapbiomas_", basin_id, ".tif")), overwrite = TRUE)

    }

tictoc::toc() 

```

## MODIS cropping

```{r }

# MODIS raster for whole MT
modis_full <- rast(file.path(dir_data, "pangaea", "panga_braz84_mt.tif"))

# Cropping
tictoc::tic()

for (basin_id in basin_select$HYBAS_ID){
  
  ligne <- which(basin_id==basin_select$HYBAS_ID)
  
  modis_crop <- terra::crop(modis_full,basin_select[ligne,])
  modis_mask <- terra::mask(modis_crop,vect(basin_select[ligne,]))
  modis_mask_utm <- terra::project(modis_mask,"+init=epsg:32721",method="ngb")

  WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]

  terra::writeRaster(modis_mask_utm, file.path(WD.tmp, paste0("modis_", basin_id, ".tif")), overwrite = TRUE)

}

tictoc::tic()

```

## Water surfaces cropping

1. SIMPLE RIOS 

```{r }

rios <- st_read(file.path(dir_data, "water_surface", "rios_simples", "rios_simple84.shp"))

tictoc::tic()

  no_cores <- detectCores()
  cl <- makeCluster(no_cores-10) # setting up number of cores
  registerDoParallel(cl) # parallelizing on them
  
  foreach(basin_id=basin_select$HYBAS_ID, .packages=c('sf')) %dopar%  { #
    
    ligne <- which(basin_id==basin_select$HYBAS_ID)

    crop_list <- st_intersects(basin_select[ligne,],rios)
    crop_shp <- hydronetwork[unlist(crop_list),]
    crop.utm <- st_transform(crop_shp, crs="EPSG:32721") 
    
    WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]

    st_write(crop.utm, file.path(WD.tmp, paste0("riossimple_",basin_id,".shp")), delete_layer = TRUE)
  
   }
  
  stopCluster(cl)
  
tictoc::toc() 

```

## Water surfaces cropping

2. POLY RIOS 

!!! There are invalid geometries. Error not solved.

```{r }

polynetwork <- st_read(file.path(dir_data, "water_surface", "rios_poly", "output_hidro_poly.shp"))

tictoc::tic()
  no_cores <- detectCores()
  cl <- makeCluster(no_cores) # setting up number of cores
  registerDoParallel(cl) # parallelizing on them
  
  foreach(basin_id=basin_select$HYBAS_ID, .packages=c('sf')) %dopar%  { #
    
    ligne <- which(basin_id==basin_select$HYBAS_ID)
    
    #if(polynetwork[ligne,]!=0){
      
      crop_list <- st_intersects(basin_select[ligne,],polynetwork)
      crop_shp <- polynetwork[unlist(crop_list),]
      crop.utm <- st_transform(crop_shp, crs="EPSG:32721") 
      
      WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]
      st_write(crop.utm, file.path(WD.tmp, paste0("riospoly_",basin_id,".shp")), delete_layer = TRUE)

    #}
  
   }
  
  stopCluster(cl)
tictoc::toc() 

```


## Water surfaces cropping

3. NASCENTES

```{r }

nascente <- st_read(file.path(dir_data, "water_surface", "nascentes", "nascente84.shp"))

tictoc::tic()
  no_cores <- detectCores()
  cl <- makeCluster(no_cores) # setting up number of cores
  registerDoParallel(cl) # parallelizing on them
  
  foreach(basin_id=basin_select$HYBAS_ID, .packages=c('sf')) %dopar%  { #
      
      crop_list <- st_intersects(basin_select[ligne,],nascente)
      crop_shp <- nascente[unlist(crop_list),]
      crop.utm <- st_transform(crop_shp, crs="EPSG:32721") 

      WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]
      st_write(crop.utm, file.path(WD.tmp, paste0("nascente_",basin_id,".shp")), delete_layer = TRUE)
  
   }
  
  stopCluster(cl)
tictoc::toc() 

```

## Water surfaces cropping

4. RESERVATORIOS

```{r }

reserv <- st_read(file.path(dir_data, "water_surface", "lago", "input_lago_reservatorio_icv.shp"))

tictoc::tic()
  no_cores <- detectCores()
  cl <- makeCluster(no_cores) # setting up number of cores
  registerDoParallel(cl) # parallelizing on them
  
  foreach(basin_id=basin_select$HYBAS_ID, .packages=c('sf')) %dopar%  { #

      crop_list <- st_intersects(basin_select[ligne,],reserv)
      crop_shp <- reserv[unlist(crop_list),]
      crop.utm <- st_transform(crop_shp, crs="EPSG:32721") 
    
      WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]
      st_write(crop.utm, file.path(WD.tmp, paste0("reserv_",basin_id,".shp")), delete_layer = TRUE)
  
   }
  
  stopCluster(cl)
tictoc::toc() 

```






