---
title: "Landscape metrics on Mapbiomas land use"
output: html_document
---

We compute landscape metrics using the package "landscapemetrics", which saves results as a data frame. We are looping on basins, so at each run one data frame is built and saved in the specific basin folder. 
Metrics are computed at basin level (1), spring buffer level (2, buffer size should be specified in 'parameters'), and stream riparian buffer level (3, buffer size as selected in 'parameters').

## Directories

```{r }

if ((Sys.info()["nodename"]) == "COP026") {
  dir_data <- "C:/Users/arvor_d/Documents/workwork/data"
  dir_plot <- "C:/Users/arvor_d/Documents/workwork/plot"
} else if ((Sys.info()["nodename"]) == "COSTELSV6") {
  dir_data <- "F:/kamir_e/$data"
  dir_plot <- "F:/kamir_e/$plot"
}

```

## Library

```{r }

library(plyr)
library(tidyverse)
library(tidyr)
library(dplyr)
library(foreach)
library(doParallel)
library(maps)
library(landscapemetrics)
library(sf)
library(terra)

```

## Parameters

```{r }

year <- 2019
time_span <- c(1985:2019)
y <- which(year==time_span)
tampon <- 100 #100, 250, 500 reste a faire 250

basin_select <- st_read(file.path(dir_data, "hydroshed", "basin_select.shp"))

```

## 1. Computing metrics on WHOLE BASIN

```{r }

tictoc::tic()

  no_cores <- detectCores()
  cl <- makeCluster(no_cores) # setting up number of cores
  registerDoParallel(cl) # parallelizing on them
  
  foreach(basin_id=basin_select$HYBAS_ID, .packages=c('landscapemetrics', 'terra', 'raster')) %dopar%  { 

  # directory
  WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]

  # loading landuse data
  mapbiomas <- rast(file.path(WD.tmp, paste0("mapbiomas_", basin_id, ".tif")))
  
  #computing landscape metrics at basin scale (MapBiomas)
  mapbiomas.basin.lsm = calculate_lsm(mapbiomas,level="class",metric = c("ca","pland","np"),directions =8)
  
  mapbiomas.basin.df = as.data.frame(mapbiomas.basin.lsm)

  save(mapbiomas.basin.df, file = file.path(WD.tmp, paste0("mapbiomas_lsm_",basin_id,".RData")))

}

  stopCluster(cl)
tictoc::toc()

```

## 2. Computing metrics on SPRING BUFFER

We assess 3 buffer size: 100, 250, 500 meters

```{r }

tictoc::tic()

  no_cores <- detectCores()
  cl <- makeCluster(no_cores/2) # setting up number of cores
  registerDoParallel(cl) # parallelizing on them
  
  foreach(basin_id=basin_select$HYBAS_ID, .packages=c('landscapemetrics', 'terra', 'raster', 'sf')) %dopar%  { 

  # directory
  WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]
  
  # loading landuse data
  mapbiomas <- rast(file.path(WD.tmp, paste0("mapbiomas_", basin_id, ".tif")))
  nascente <- st_read(file.path(WD.tmp,paste0("nascente_",basin_id,".shp"))) 
  
  if(nrow(nascente)>0){
    
    nascente.buf = st_buffer(nascente, dist = tampon)
    nascente.buf.uni = st_union(nascente.buf)
    mapbiomas_buf = terra::mask(mapbiomas,vect(nascente.buf.uni))
  
    #computing landscape metrics at basin scale (MapBiomas)
    mapbiomas.basin.lsm = calculate_lsm(mapbiomas_buf,level="class",metric = c("ca","pland","np"),directions =8)
    
    mapbiomas.basin.df = as.data.frame(mapbiomas.basin.lsm)
    
  }
  
  else {mapbiomas.basin.df <- "nonascente"}
  
  save(mapbiomas.basin.df, file = file.path(WD.tmp, paste0("mapbiomas_lsm_buf",tampon, "_",basin_id,".RData")))

}

  stopCluster(cl)
tictoc::toc()

```

## Computing metrics on STREAM RIPARIAN BUFFER

We assess 3 buffer size: 100, 250, 500 meters
Warning: errors on around 10 basins where streams files are wrong.

```{r }

j=0

tictoc::tic()

  no_cores <- detectCores()
  cl <- makeCluster(no_cores) # setting up number of cores
  registerDoParallel(cl) # parallelizing on them
  
foreach(basin_id=basin_select$HYBAS_ID, .packages=c('landscapemetrics', 'terra', 'raster', 'sf')) %dopar%  { 

  j=j+1
  # directory
  WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]
  
  # loading landuse data
  mapbiomas <- rast(file.path(WD.tmp, paste0("mapbiomas_", basin_id, ".tif")))
  rios <- st_read(file.path(WD.tmp,paste0("riossimple_",basin_id,".shp"))) 
  
  error_test <- tryCatch(expr=st_buffer(rios, dist = tampon), error = function(e) {an.error.occured <<- FALSE}, silent=TRUE) 
  
  if(class(error_test)[1]=='sf' & nrow(rios)>0){
    
    rios.buf = st_buffer(rios, dist = tampon)
    rios.buf.union = st_union(rios.buf)
    mapbiomas_buf = terra::mask(mapbiomas,vect(rios.buf.union))
    
    #computing landscape metrics at basin scale (MapBiomas)
    mapbiomas.basin.lsm = calculate_lsm(mapbiomas_buf,level="class",metric = c("ca","pland","np"),directions =8)
      
    mapbiomas.basin.df = as.data.frame(mapbiomas.basin.lsm)
      
  
  } else {mapbiomas.basin.df <- "rios_error"}
  
  save(mapbiomas.basin.df, file = file.path(WD.tmp, paste0("lsm_rip",tampon, "_",basin_id,".RData")))

}

  stopCluster(cl)
tictoc::toc()

```