---
title: "Summarizing lsm for nascente level analysis"
output: html_document
---

We summarize landscape metrics at basin and spring buffer levels in two data frames "ggplot ready". Each of the 2 data frame gathers forest percentages in 2019 (at basin and spring level) of all basins that are either soybean or pasture specialized. The latest is set when soybean or pasture area percentage exceeds 50% of the whole watershed surface.

```{r }

if ((Sys.info()["nodename"]) == "COP026") {
  dir_data <- "C:/Users/arvor_d/Documents/workwork/data"
  dir_plot <- "C:/Users/arvor_d/Documents/workwork/plot"
} else if ((Sys.info()["nodename"]) == "COSTELSV6") {
  dir_data <- "F:/kamir_e/$data"
  dir_plot <- "F:/kamir_e/$plot"
}

```

## Library

```{r }

library(plyr)
library(tidyverse)
library(tidyr)
library(dplyr)
library(maps)
library(ggplot2)
library(ggmap)
library(sf)
library(viridis)

```

## PARAMETERS

```{r }

# foret = 3, savanna = 4, pasture = 15, soybean = 39, other temp.crops = 41, per.crops = 36

time_laps <- c(1985:2019)
year=2019
y <- which(time_laps==year)
tampon = 100

basin_select <- st_read(file.path(dir_data, "hydroshed", "basin_select.shp"))

```

## LOADING & MERGING files

We filter and merge into dataframes landscape metrics output

```{r }

list_basin <- list()
list_nasc <- list()

j=0

for (basin_id in basin_select$HYBAS_ID){
  
j =j+1

    WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]
    
    list_nasc[[j]] <- get(load(file=file.path(WD.tmp, paste0("mapbiomas_lsm_buf",tampon,"_",basin_id,".RData"))))
    
    if(list_nasc[[j]]=="nonascente"){
      list_nasc[[j]] <- NA
      list_basin[[j]] <- NA
    }
    
    else {list_basin[[j]] <- get(load(file=file.path(WD.tmp, paste0("mapbiomas_lsm_",basin_id,".RData")))) %>% mutate(annee=year, ID=basin_id)
    list_nasc[[j]] <- list_nasc[[j]] %>% dplyr::select(-id) %>% mutate(annee=year, ID=basin_id) }
    

}

df_basin <- do.call("rbind",list_basin) %>% filter(layer==y)
df_nasc <- do.call("rbind",list_nasc) %>% filter(layer==y)

```

## SETTING up table of forested area table

It is set up in order to be directly used for boxplotting


```{r }

# whole basin forestd area
list_forest_basin <- list()

# forested area around nascentes
list_forest_nasc <- list()

j=0

for (basin_id in basin_select$HYBAS_ID){
  
  perc_past <- (df_basin %>% filter(ID==basin_id, class==15, metric=='pland'))$value
  perc_crop <- (df_basin %>% filter(ID==basin_id, class==39, metric=='pland'))$value 
  
  if(is_empty(perc_past)){perc_past=0}
  if(is_empty(perc_crop)){perc_crop=0}
  
  if(perc_past>=50){
    j=j+1
    list_forest_basin[[j]] <- df_basin %>% filter(ID==basin_id, class == 3, metric=='pland') %>% mutate(maj='pasture')
    list_forest_nasc[[j]] <- df_nasc %>% filter(ID==basin_id, class == 3, metric=='pland') %>% mutate(maj='pasture')
    }
  
  if(perc_crop>=50){
    j=j+1
    list_forest_basin[[j]] <- df_basin %>% filter(ID==basin_id, class == 3, metric=='pland') %>% mutate(maj='soybean')
    list_forest_nasc[[j]] <- df_nasc %>% filter(ID==basin_id, class == 3, metric=='pland') %>% mutate(maj='soybean')
  }
  
}


df_basin_foret <- do.call("rbind",list_forest_basin) %>% mutate(annee=year) %>% dplyr::select(-id)
df_nasc_foret <- do.call("rbind",list_forest_nasc) %>% mutate(annee=year) 

save(df_basin_foret, file=file.path(dir_plot, paste0("df_basin_foret4nasc_",tampon,".RData")))
save(df_nasc_foret, file=file.path(dir_plot, paste0("df_nasc_foret_", tampon, ".RData")))


```


