---
title: "Summarizing landscape metrics to further plot forestation %"
output: html_document
---

We build new data frames (1 for riparian level, 1 for basin level) giving % forest at the selected level, and main farming mode at basin level. When more than 60% of deforested area (basin level) is covered by soybean (alternatively pasture), crop is defined as the main farming mode (alternatively pasture).

## Directories

```{r }

if ((Sys.info()["nodename"]) == "COP026") {
  dir_data <- "C:/Users/arvor_d/Documents/workwork/data"
  dir_plot <- "C:/Users/arvor_d/Documents/workwork/plot"
} else if ((Sys.info()["nodename"]) == "COSTELSV6") {
  dir_data <- "F:/kamir_e/$data"
  dir_plot <- "F:/kamir_e/$plot"
}

```

## Library

```{r }

library(plyr)
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)
library(sp)
library(sf)

```

## PARAMETERS

```{r }

# foret = 3, savanna = 4, pasture = 15, soybean = 39, other temp.crops = 41, per.crops = 36

time_laps <- c(1985:2019)
year=2019
y <- which(time_laps==year)
tampon = 100

basin_select <- st_read(file.path(dir_data, "hydroshed", "basin_select.shp"))

```

## LOADING & MERGING files

We filter and merge into dataframes landscape metrics output

```{r }

list_basin <- list()
list_rios <- list()

j=0

for (basin_id in basin_select$HYBAS_ID){
  
j =j+1

    WD.tmp = list.files(path=dir_data, pattern = paste0("_",basin_id), full.names = TRUE)[1]
    
    list_rios[[j]] <- get(load(file=file.path(WD.tmp, paste0("lsm_rip",tampon, "_",basin_id,".RData"))))
    
    if(list_rios[[j]]=="rios_error"){
      list_rios[[j]] <- NA
    }
    
    else {list_rios[[j]] <- list_rios[[j]] %>% dplyr::select(-id) %>% mutate(annee=year, ID=basin_id) }
    

}

df_rios <- do.call("rbind",list_rios) %>% filter(layer==y)

```

## SETTING up table of forested area table

It is set up in order to be directly used for boxplotting


```{r }

df_lsm_relatif <- get(load(file = file.path(dir_data, 'processed', paste0("df_lsm_relatif.RData"))))
df_lsm_relatif2 <- df_lsm_relatif %>% rename(value=for.nat, ID=hybas_id)
  
# whole basin forestd area
list_forest_basin <- list()

# forested area around nascentes
list_forest_rios <- list()

j=0

for (basin_id in basin_select$HYBAS_ID){
  
  perc_past <- (df_lsm_relatif2 %>% filter(ID==basin_id))$past.rel
  perc_crop <- (df_lsm_relatif2 %>% filter(ID==basin_id))$soy.rel
  
  if(perc_past>=60){
    j=j+1
    list_forest_basin[[j]] <- df_lsm_relatif2 %>% filter(ID==basin_id) %>% mutate(maj='pasture')
    list_forest_rios[[j]] <- df_rios %>% filter(ID==basin_id, class == 3, metric=='pland') %>% mutate(maj='pasture')
    }
  
  if(perc_crop>=60){
    j=j+1
    list_forest_basin[[j]] <- df_lsm_relatif2 %>% filter(ID==basin_id) %>% mutate(maj='soybean')
    list_forest_rios[[j]] <- df_rios %>% filter(ID==basin_id, class == 3, metric=='pland') %>% mutate(maj='soybean')
  }
  
}

df_basin_foret <- do.call("rbind",list_forest_basin) %>% mutate(annee=year) 
df_rios_foret <- do.call("rbind",list_forest_rios) %>% mutate(annee=year) 

save(df_basin_foret, file=file.path(dir_plot, paste0("df_basin_foret4rios_",tampon,".RData")))
save(df_rios_foret, file=file.path(dir_plot, paste0("df_rios_foret_", tampon, ".RData")))

```


